1. If the patient has a leg injury, paracetamol is not necessary.
% paracetamol missing from PWN,  conditional
2. Symptoms of flu include fever and cough.
% ok
3. symptoms of migraine may involve infarction and seizures
% ok, modal may
4. fever is a symptom in more than 80 percent of West Nile virus infection patient
% long MWE and numerical reasoning
5. Severe symptoms and signs may include stiff neck, sleepiness, disorientation, coma, tremors, convulsions, and paralysis.
% ok long list
6. cholera symptoms are watery diarrhea (sometimes in large volumes), Fishy odor to stools, Vomiting, Rapid heart rate, Loss of skin elasticity (washer woman hands sign; see figure 2), Dry mucous membranes (dry mouth), Low blood pressure.
% doesn't complete (long list? or parenthesis?)
7. Constitutional symptoms such as fatigue, fever, and weight loss are present in most lupus patients.
%Constitutional is not proper and not cardinal? 6 senses of adjective, 2 equally good? what to do about most?
8. Arthritis occur in over 90 percent of patients with SLE
% numerical reasoning, abbreviations (SLE=Systemic lupus erythematosus) arthritis is not a proper noun, just the beginning of the sentence
9. Most patients have skin and mucous membrane lesions 
% parsing "mucous membrane" lesions!
10. West Nile fever includes fever, headache, malaise, back pain, myalgias, and anorexia.
% "West Nile" (not found) WN fever needs to be connected to West Nile virus? why anorexia was not found? it's in PWN
11. A maculopapular rash appears in all patients.
% MWE: "maculopapular rash" in Wikipedia, maculopapular not in PWN
12. neurological manifestations include tremor, myoclonus, rigidity, postural instability, and bradykinesia.
% bradykinesia. missing, 
13. When distal DVT is not identified, no further testing is required;
% abbrev DVT=Deep vein thrombosis
14. We prefer to obtain a liver biopsy in all patients with suspected autoimmune hepatitis.
% "suspected" should create a context
15. A variety of metabolic abnormalities can occur in hypothyroidism, including hyponatremia, hyperlipidemia, anemia, and high serum muscle enzyme concentrations.
% nothing missing in WN, but "can" context?
16. Arthritis and arthralgias occur in over 90 percent of patients with SLE
% only SLE missing, even if emacs doesn't recognize arthralgias, WN does
17. Most patients have skin and mucous membrane lesions at some point during the course of the disease.
% parsing doesn't get "mucous mebrane lesions"
18. Several vascular abnormalities including Raynaud phenomenon, vasculitis, and thromboembolic disease can occur in SLE patients.
% mwe:Raynaud phenomenon missing, thromboembolic missing
19. Renal involvement is clinically apparent in approximately 50 percent of patients.
% numerical reasoning, mwe: renal involvement 
20. Cardiac manifestations include pericarditis (with or without an effusion), verrucous, (Libman-Sacks) endocarditis, myocarditis, and coronary artery disease.
% not completing, parenthesis? long list?
21. Any structure of the eye can be involved in SLE.
% any quantifier?
22. A maculopapular rash appears in up to one half of such patients.
%as before: maculopapular rash (https://en.wikipedia.org/wiki/Maculopapular_rash), numerical reasoning
23. Encephalitis that is associated with muscle weakness and flaccid paralysis is particularly suggestive of WN virus infection.
%missing WN and flaccid??? why? it's in WN!
24. Other neurologic manifestations include tremor, myoclonus, and Parkinsonian features such as rigidity, postural instability, and bradykinesia.
%as before bradykinesia, but also parkinsonian(??) and neurologic?
25. In patients with neurologic symptoms, a lumbar puncture should also be performed.
% "lumbar" missing? "also" is a problem
26. We prefer to obtain a liver biopsy in all patients in whom autoimmune hepatitis is suspected.
% pronoun "we" missing
27. Evaluation of postpartum hypopituitarism should be performed whenever it is suspected after a delivery associated with unusually heavy blood loss.
% whenever, postpartum,  hypopituitarism missing conditional
28. DVT is diagnosed if ultrasonography is positive.
%abreviation DVT missing, conditional missing